DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/background.tex
integrate related work with background section
revise conclusion
abstract

\section{Background} \label{sec:background}

In this section, we provide background on the application of deep
learning in robotics, particularly autonomous vehicles.

>>>>

\section{Background and Related Work} \label{sec:background}

In this section, we provide background and related work on the
application of deep learning in robotics, particularly autonomous
vehicles.

### 2017-10-06 paper/main.tex
integrate related work with background section
revise conclusion
abstract

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Author One, Author Two\\
\{author1,author2\}@ku.edu\\
University of Kansas, USA\\ 
}

\maketitle
\thispagestyle{empty}
\begin{abstract}
Abstract goes here.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{reference}
\end{document}

>>>>

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Michael Garrett Bechtel, Elise McEllhiney, Heechul Yun\\
\{m783b224, e908m429, heechul.yun\}@ku.edu\\
University of Kansas, USA\\ 
}

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove public roads using a deep convolutional network (CNN), which
takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 24K
parameters---and can be trained to drives itself using a small web
camera in real-time on a modest Raspberry Pi 3 quad-core computing
platform. Using DeepPicar, we analyze Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's deep learning control system
as a workload.
We find all tested platforms, including the Pi3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

%% In order to effectively research autonomous vehicles, a real-time
%% capable platform is required. Such platforms can be hard to obtain, or
%% build, as the necessary components can be expensive. In this paper,
%% we present a low-cost alternative platform that utilizes a Raspberry
%% Pi 3 Model B, along with a single external camera sensor, to perform
%% all necessary self-driving operations. A convolutional neural network
%% (CNN) is employed and trained with input from a human driver to
%% navigate a custom made track. We display the real-time efficacy of our
%% platform in experiments with varying amounts of computational resources
%% and/or intensive AI workloads. To gain a better understanding of our
%% platform's potential, we compare it to other embedded computing
%% platforms to determine which are suitable for autonomous driving
%% research.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
% \input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{abbrv}
\bibliography{reference}

\appendix
\input{appendix}
\end{document}
